Next Trippy Structures\thanks{Supported by organization x.}

### 2019-01-17 paper.tex
Common structures explained

All of them stored explicitly except for $initialTime$, which is compressed with sampled ZSTD.

>>>>

With the exception of $initialTime$, all these structures are small enough to be represented using plain fixed-length integer arrays. In the case of $initialTime$, its size naturally grows with the amount of trips that are indexed, thus there is a motivation to reduce its size, which can be easily achieved with any technique that works on posting lists or sequences of strictly increasing numbers. In our work we used a simplified Vbyte+ANS compression described in \cite{moffat2017ans} using the Zstd library\footnote{https://github.com/facebook/zstd}. In order to facilitate searches and random access, we introduced fixed-length samples on configurable intervals.

An example of these structures interacting together can be found at the Algorithm~\ref{alg:jcodes}, the the function \FuncSty{lower\_bound} is a binary search that returns the index of the first occurrence that is no lesser than the queried value, while \FuncSty{upper\_bound} returns the index of the last no greater occurrence.
